\begin{thebibliography}{9}
	
	\bibitem{hawkins}
	 D. M. Hawkins, \textit{Identification of outliers}. Springer, 1980, vol. 11.
	
	\bibitem{a}V. Chandola, A. Banerjee, and V. Kumar, “Anomaly detection: A
	survey,” ACM \textit{Computing Surveys (CSUR)}, vol. 41, no. 3, pp. 1–58, 2009.
	
	\bibitem{b}Markus M. Breunig, Hans-Peter Kriegel, Raymond T. Ng, and Jörg Sander. 2000. LOF: identifying density-based local outliers. SIGMOD Rec. 29, 2 (May 2000), 93-104. 
	
	\bibitem{c}D. Pokrajac, A. Lazarevic, and L. J. Latecki, “Incremental local outlier
	detection for data streams,” in Proc. IEEE Symp. Comput. Intell.
	Data Mining, 2007.
	
	\bibitem{d}M. Salehi, C. Leckie, J. C. Bezdek, T. Vaithianathan and X. Zhang, "Fast Memory Efficient Local Outlier Detection in Data Streams," in IEEE Transactions on Knowledge and Data Engineering, Dec. 1 2016.
	
	\bibitem{e}Fabrizio Angiulli and Fabio Fassetti. 2009. DOLPHIN: An efficient algorithm for mining distance-based outliers in very large datasets. ACM Trans. Knowl.
	
	\bibitem{f}J.Tang, Z. Chen, AW. Fu, D.W. Cheung, Capabilities of outlier detection schemes in large datasets, framework and methodologies Knowledge and Information Systems 11(1), 2006, pp. 45–84.
	
	\bibitem{ca1}
	C. Warrender, S. Forrest, and B. Pearlmutter, “Detecting intrusions using system calls:
	Alternative data models,” in Security and Privacy, 1999. Proceedings of the 1999 IEEE
	Symposium on. IEEE, 1999, pp. 133–145.
	
	\bibitem{ca2}
	C. C. Noble and D. J. Cook, “Graph-based anomaly detection,” in Proceedings of the ninth ACM
	SIGKDD international conference on Knowledge discovery and data mining. ACM, 2003, pp.
	631–636.
	
	\bibitem{ca3}
	S. Shekhar, C.-T. Lu, and P. Zhang, “Detecting graph-based spatial outliers: algorithms and
	applications (a summary of results),” in Proceedings of the seventh ACM SIGKDD international
	conference on Knowledge discovery and data mining. ACM, 2001, pp. 371–376.
	
	\bibitem{contextual}
	X. Song, M. Wu, C. Jermaine, and S. Ranka, “Conditional anomaly detection,” Knowledge and
	Data Engineering, IEEE Transactions on, vol. 19, no. 5, pp. 631–645, 2007.
	
	\bibitem{fraud}
	R. J. Bolton, D. J. Hand et al., “Unsupervised profiling methods for fraud detection,” Credit
	Scoring and Credit Control VII, pp. 235–255, 2001.
	
	\bibitem{medical}
	J. Lin, E. Keogh, A. Fu, and H. Van Herle, “Approximations to magic: Finding unusual medical
	time series,” in Computer-Based Medical Systems, 2005. Proceedings. 18th IEEE Symposium on.
	IEEE, 2005, pp. 329–334.
\end{thebibliography}

