\thispagestyle{empty} 
\SpecialTitle{Acknowledgment}
\noindent 

First of all I would like to express my deepest respect and gratitude towards my supervisor,
Dr. Bidyut Kumar Patra, who guided me throughout the past year as I was working on my
final year project. I’d like to thank him for introducing me to the field of data science and
machine learning, and giving me the opportunity to work under him in this urban computing
project. His confidence in me and his nature of being a strict taskmaster has proven to bring
out the best version of myself multiple times while working on this project. His focus on
clarity of thought and topic is unmatched, which has helped me be very clear about the
subject from the get-go. His expertise in his field has proved to be of immense help to me
during the course of this thesis work.

\par

I would also like to thank the PhD researchers and my fellow Masters students who made our
laboratory so conducive to producing quality research work by setting benchmarks at every
stage. They have been very helpful whenever I needed any help with understanding the
content matter or implementations. I’d also like to thank my peers who have never hesitated
while extending a helping hand whenever I was in need of guidance or support.
Along with my thesis supervisor, all my faculties have played an important role in shaping
me concepts over the past five years and made this project possible. Hence I’d like to
extend my sincere thanks to the Prof. Durga Prasad Mohapatra, Head of the Department of
Computer Science and Engineering and all department faculties for their timely co-operation
and enthusiasm in giving invaluable feedback for my project work.
My project would not be complete had it not been for the researchers and data scientists
in working in this field and continue on their path to make the world a better place to live
with the help of their research. It gives me great satisfaction that I am able to work in the
same field as them, and would like to thank them for their well-documented researches. I
apologize, in the event I have overlooked anybody in this section.

\vspace{15mm}
\begin{minipage}{.45\linewidth}
\begin{flushleft}
May 10, 2018\\
NIT Rourkela
\end{flushleft}
\end{minipage}
\begin{minipage}{.45\linewidth}
\begin{flushright}
\textit{Koshal Kumar Garg}\\
Roll Number: 114CS0100
\end{flushright}
\end{minipage}